Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-11 doc/main_jfm.tex
Peter working on revision

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{conclusion}Conclusion}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figure13_Wrapper.pdf}
  \caption{\label{figure13} Comparisons between the proposed model and a conitnuum model in 
  two JP vesicle simulations. 
  $d_{1,2}$ is the distance between two centroids of JP vesicles. The thick curves plot the trajectories
  of $d_{1,2}$ generated by the continuum model and the thin curves are computed from using
  the proposed model.}
\end{figure}

\ReviewerOne{Since the behavior of the suspended JP vesicles has similarities to the numerical 
results generated by using the algorithm in \cite{qua-vee-you2019} (refer to all figure insets in 
Figure~\ref{figure10} and Figure~\ref{figure12}). Figure~\ref{figure13} shows trajectory 
comparisons between the proposed model and the continuum modeling for both shear flow and
extensional flow cases in two vesicle simulations. The quantity $d_{1,2}$ represents the distance
between two centroids of JP vesicles. The centroid positions are identical for both models and the
geometry in the continuum model is created along the midplane locations of JP vesicles and the initial
reduced area is matched. Panel (a) shows that the results of continuum model does not have a 
periodic motion and two vesicles flow apart after 1.5 $\mu$s. Panel (b) shows that the results of
continuum model has similar trend of dynamics with one in the proposed model.}

%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{conclusion}Conclusion}
